Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
ok

@@

```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingovertime-1.png
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)

df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(n = n())
p <- ggplot(df2, aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = catalog)) +
     geom_point(aes(shape = catalog), size = 3) +     
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle("Overall publishing activity")
print(p)
```

@@

Comparison of printing activity in

@@

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=8, fig.height=6, fig.show="hold", out.width="430px"}
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png
selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) # %>%
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = spread(df2, publication_decade, n, fill = 0)
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {

@@

## Publishers Finland

Number of unique publishers in top publication places over time (Fennica)

@@

## Publishers Kungliga

@@

```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15, fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png

place <- "Turku"
df = df0

@@

@@

```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}

@@

@@

## Riksdagar 2

Focus on Gävle (gray) during riksdagar. Gävle has `r sum("Gävle" %in% fen$publication_place)` occurrences in Fennica, hence not included here. The figure on Gävle is based on Kungliga.

```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, out.width="430px"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/riksdar2-1.png

@@

## Book printing in Finland / Language

```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/language1-1.png
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/language1-2.png

  df <- df0
  df <- df %>% filter(catalog == catalogue)

langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0

}
dfl$language <- factor(dfl$language, levels = langs)

@@

# PAPER CONSUMPTION
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
print(p)

@@

```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
for (catalogue in c("Fennica", "Kungliga")) {

@@

}
dfl$language <- factor(dfl$language, levels = langs)

@@

```{r topics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
catalogue <- "Fennica"
langs <- c("Finnish", "Swedish", "Latin", "German", "Other")

@@

  lang <- paste("language.", langs, sep = "")
  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
  dfl <- NULL
  for (lan in lang) {
    # Classify a document to the specifed language
    # If document is assigned with languages, each case is considered
    # so one doc may have multiple entries corresponding to different languages
    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
    # Combine data frames for specified languages
    dflsub <- filter(df, df[[lan]])
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
  dfl$language <- factor(dfl$language, levels = langs)
  df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

Sama kuin edellä, mutta asiasanat tässä: hautajaiset;häät;juhlamenot.

```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics2-2.png

@@

Hartauskirjallisuudesta ks. Osmo Tiililä, Rukoilevaisten kirjoja, 1961.

General analysis with all documents combined:

```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics3-2.png

@@

langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  # Classify a document to the specifed language
  # If document is assigned with languages, each case is considered
  # so one doc may have multiple entries corresponding to different languages
  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
  # Combine data frames for specified languages
  dflsub <- filter(df, df[[lan]])
  dflsub$language <- gsub("language.", "", lan)
  dfl <- bind_rows(dfl, dflsub)
}
dfl$language <- factor(dfl$language, levels = langs)

@@

#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-2.png
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-4.png
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-6.png
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-8.png
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-14.png

df <- df0 %>% filter(catalog == catalogue)
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}
dfl$language <- factor(dfl$language, levels = names(table(dfl$language)))
# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r topics-102, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel = c("oppihistoria","antiikki","historia")
# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r topics-103, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r topics-104, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel = c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia")
# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/LIBER-13-2.png
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption (km2)")
  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
  print(p)
}
```

@@

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/201606krakow-turkuvsother-2.png

@@

>>>>

# Set locale
Sys.setlocale(locale="UTF-8")

@@

```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=6}
library(devtools)
install_github("ropengov/gisfin")

# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingovertime-1.png
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)

df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(n = n())
p <- ggplot(df2, aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = catalog)) +
     geom_point(aes(shape = catalog), size = 3) +     
     ylab("Title count (n)") + xlab("Publication year") #+  
     # ggtitle("Overall publishing activity")
print(p)
```

@@

@@

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="150px"}
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png
selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) # %>%
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = spread(df2, publication_decade, n, fill = 0)
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {

@@

## Unique publishers in top publication places over time

@@

@@

```{r publishers3-finland-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=13, out.width="150px", fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png

place <- "Turku"
catalogue = "Fennica"
df = df0

@@

```{r publishers3-finland-kungliga, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=13, out.width="150px", fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png
catalogue = "Kungliga"
place <- "Turku"
df = df0

# TITLE COUNT
theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
       xlab("Publication year") +
       ylab("Title count (n)") +        
       ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
print(p)
```

@@

```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width="150px", fig.show="hold"}

@@

  # Selected ones
  df$publisher[df$publisher == ""] = "Other"
  top <- names(top(df, "publisher", 5))
  df$publisher[!df$publisher %in% c(top, "")] <- "Other"
  df$publisher <- factor(df$publisher, levels = c(top, "Other"))

@@

## Gävle in Riksdagar

Gävle (gray) during riksdagar (Kungliga)

```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/riksdar2-1.png

@@

## Book printing in Finland / Fennica

```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="150px", fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/language1-1.png
catalogue = "Fennica"
df <- df0
langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  # Classify a document to the specifed language
  # If document is assigned with languages, each case is considered
  # so one doc may have multiple entries corresponding to different languages
  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
  # Combine data frames for specified languages
  dflsub <- filter(df, df[[lan]])
  dflsub$language <- gsub("language.", "", lan)
  dfl <- bind_rows(dfl, dflsub)

}

# ----------------------------------

df <- dfl %>% filter(catalog == catalogue)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

## Book printing in Finland / Kungliga

```{r language1-kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="150px", fig.show="hold"}
catalogue = "Kungliga"
  df <- dfl %>% filter(catalog == catalogue)
  df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="150px", fig.show="hold"}
for (catalogue in c("Fennica", "Kungliga")) {

@@

}

@@

```{r topics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
catalogue <- "Fennica"
langs <- c("Finnish", "Swedish", "Latin", "German", "Other")

@@

  lang <- paste("language.", langs, sep = "")
  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
  dfl <- NULL
  for (lan in lang) {
    # Classify a document to the specifed language
    # If document is assigned with languages, each case is considered
    # so one doc may have multiple entries corresponding to different languages
    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
    # Combine data frames for specified languages
    dflsub <- filter(df, df[[lan]])
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
  df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

hautajaiset;häät;juhlamenot.

```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics2-2.png

@@

```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics3-2.png

@@

langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  # Classify a document to the specifed language
  # If document is assigned with languages, each case is considered
  # so one doc may have multiple entries corresponding to different languages
  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
  # Combine data frames for specified languages
  dflsub <- filter(df, df[[lan]])
  dflsub$language <- gsub("language.", "", lan)
  dfl <- bind_rows(dfl, dflsub)
}

@@

df <- df0 %>% filter(catalog == catalogue)
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}
# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r topics-102, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel = c("oppihistoria","antiikki","historia")
# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r topics-103, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r topics-104, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel = c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia")
# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

# Selected catalogue with selected topics
df = dfl
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
df <- df %>% filter(hit)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/LIBER-13-2.png
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption (km2)")
  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
  print(p)
}
```

@@

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/201606krakow-turkuvsother-2.png

@@

## Thanks !

- Academy of Finland
- University of Helsinki
